Generative Adversarial Networks

### 2017-12-06 cs6735/assignment/report.tex
finished data section

\usepackage{natbib}
\usepackage{graphicx}
\usepackage[options ]{algorithm2e}
\usepackage{parskip}

@@

\section{Introduction}
This report details the experimental study conducted for the CS6735 programming project. Six machine learning algorithms were implemented, including both regular and ensemble learning algorithms. Each was evaluated on five datasets from the UCI machine learning data repository using 10 times 5-fold cross validation. The technical details of the implementation will be described and the results will be analyzed.

@@

\subsection{Naïve Bayes}
The Naive Bayes algorithm is implemented as described in \cite{Mitchell:1997:ML:541177}. This algorithm is named due its assumption of conditional independance amongst each attribute:

@@

and its application of Bayes thereom:

@@

Naive Bayes is a practical learning algorithm, receives relatively good results given its preference bias and is easy to implement. This algorithm naturally handles both catigorical and continuous data (given a prior is assumed). For each continuous attribute, a Gaussian distribution was assumed. The final algorithm implemented was:

$$\hat{y}= \underset{k\;\in\;\{1,..K\}} {\mathrm{argmax}} \;\;P(v_k)\prod_{i=1}^mp\left(a_i\;|\;v_k\right)\prod_{j=m}^nP\left(a_j\;|\;v_k\right)\;\;$$

where $P$ is the probability, $p$ is the gaussian probability density function and $K$ is the number of distinct targets. In this equation, the first m attributes are continous whereas the later are catigorical. During training, the data $S$ is split by lables into subsets ${S_1,...,S_n}$ where $n$ is the number of different classes. For each subset, we estimate the class probability $P(v_k)$. Subsequently, for each attribute value $a_i$ of each attribute $a$, we estimate $P(a_i|v_k)$ or $p$. We are not able to immidiately calculate $p(a_i|v_k)$ as attribute $a$ is a continous attribute.

@@

The primary part of the algorithm is to maintain a weight value $w$ for every sample within the data $S$. This value increases when the sample is misclassified and decreases when the sample is correctly classified. The target values are assumed be to in the set ${+1, -1}$. The Adaboost algorithm is easily implemented on weak learners which are parameterized by sample weights. Neither Naive Bayes or ID3 natively implement weighted training. Therefore, an alternative implementation was used where a subset of the training data is selected with replacement based on the weights. For example, if the weight vector for two samples is ${1, 2}$, the second sample is twice as likely to be picked each time.

@@

To implement multiclass adaboost, $K$ adaboost models are trained where $K$ is the total number of distint classes. For each adaboost model, one target is selected as the $+1$ adaboost target and the other become the $-1$ target. The target value associated with the most positive prediction becomes the predicted class.

\subsubsection{Adaboost on Naive Bayes}
Naive Bayes is an inherently weak learner due to its assumption of conditional independance amongst attributes. This fact introduces a large amount of preference bias which makes a Naive Bayes and ideal candidate for the Adaboost algorithm.

\subsubsection{Adaboost on ID3}
The ID3 algorithm does not introduce a large amount of preference bias and often overfits if allowed to train to completion. Therefore, to implement Adaboost on ID3, the depth of the trees were limited to one level. This type of tree is known as a \textit{decision stump}.

\subsection{Random Forest}
Random forest algorithm is a bagging algorithm which uses an ensemble of strong learners to reduce overfititng to the training set. This method contains many similarities to the adaboost algorithm as described in section \ref{adaboost}; however, no weights are used for random forests. For a predifined number of iterations, a subset of the of the training data is selected with replacement. The new training set is then used to train a decision tree to completion and added to tree is added to a list. To make a classification, each tree in the forest votes and the most common target value becomes the predicted class. As an extension of the base random forest algorithm, weights may be given to each decision tree based on their classification error during training; however, this extension was not added for this implementation.

\subsection{K-Nearest Neighbors}
The K-Nearest Neighbor algorithm is an instance based learning algorithm which makes predictions by finding the $k$ nearest neighbors of a sample $x$ and using the most common class as the predicted class for that sample. This algorithm can be used with both catigorical and continuous data. For this implementation, Euclidian distance was used for continous variables and Hamming distance was used for catigorical data.

@@

\subsection{Breast Cancer Data}
\begin{enumerate}
  \item Title: Wisconsin Diagnostic Breast Cancer
  \item Date: November 1995
  \item Number of Samples: 569
  \item Number of Attributes: 10
  \begin{tabular}{l c c c }
    Description                  & Value     & Type
    Sample Code Number           & id number & Discrete \\
    Clump Thickness              & 1 - 10    & Discrete \\
    Uniformity of Cell Size      & 1 - 10    & Discrete \\
    Uniformity of Cell Shape     & 1 - 10    & Discrete \\
    Marginal Adhesion            & 1 - 10    & Discrete \\
    Single Epithelial Cell Size  & 1 - 10    & Discrete \\
    Bare Nuclei                  & 1 - 10    & Discrete \\
    Bland Chromatin              & 1 - 10    & Discrete \\
    Normal Nucleoli              & 1 - 10    & Discrete \\
    Mitoses                      & 1 - 10    & Discrete
  \end{tabular}
  \item Class Information
  \begin{tabular}{l c c c }
    Description & Value & Likelihood
    benign      & 2     & 65.5\%
    malignant   & 4     & 34.5\%
  \end{tabular}
  \item Missing Attributes: 16
\end{enumerate}

\subsection{Car Data}
\subsection{E. Coli Data}
\subsection{Letter Recognition Data}
\subsection{Mushroom Data}

\section{Technical Details}
Any missing attribute values were each replaced with the mode of the samples of the same class. No discretization occured as all base algorithms are able to handle continuous data. For all datasets, any sort of identification number or code attributes were removed. Within the E. Coli dataset, the lip and chg catigorical attributes were also removed as they provided minimal information. Furthermore, any string values were converted to integers. For example, the ``v-high'', ``high'', ``med'' and ``low'' attribute values would have been converted to 0, 1, 2, 3 respectively.

\subsection{ID3}
\begin{tabular}{ |c|c|c| }
  Dataset            & Max Level & Minimum # of Samples \\
  Breast Cancer      & None      & SOMETHING            \\
  Car Cancer         & None      & SOMETHING            \\
  Letter Recognition & None      & SOMETHING            \\
  E. Coli            & None      & SOMETHING            \\
  Mushroom           & None      & SOMETHING
\end{tabular}

\subsection{Naive Bayes}
gaussian

\subsection{Adaboost on Naive Bayes}
number of learners

@@

\begin{enumerate}
  \item \br{Algorithm}:
  \item \br{Dataset}:
  \item \br{Model}:
  \item \br{KFold}: Implements the KFold cross validation algorithm.
  \item \br{Report}: The object returned from a k-fold cross validation test....
  \item \br{Util}: Utility functions used through the machine learning project.
\end{enumerate}

@@

\begin{enumerate}
  \item \br{Children}:
  \item \br{ID3}:
  \item \br{ID3Model}:
  \item \br{Node}:
\end{enumerate}

@@

\begin{enumerate}
  \item \br{Adaboost}:
  \item \br{AdaboostModel}:
  \item \br{Multi-Adaboost}:
  \item \br{Multi-AdaboostModel}:
  \item \br{RandomForest}:
  \item \br{RandomForstModel}:
\end{enumerate}

@@

\begin{enumerate}
  \item \br{AttributeException}:
  \item \br{DataException}:
  \item \br{FileException}:
  \item \br{PredictionException}:
\end{enumerate}

@@

\begin{enumerate}
  \item \br{MathException}:
  \item \br{Matrix}:
  \item \br{Tuple}:
  \item \br{Util}:
  \item \br{Vector}:
\end{enumerate}

@@

\begin{enumerate}
  \item \br{DistanceFunction}:
  \item \br{Euclidian}:
  \item \br{Hamming}:
\end{enumerate}

\subsubsection{distribution}
This package contains distribution implementations for the Naive Bayes classifier.

\begin{enumerate}
  \item \br{Distribution}:
  \item \br{GaussianDistribution}:
\end{enumerate}

\subsection{nb}
This package contains all of the objects associated with Naive Bayes.

\begin{enumerate}
  \item \br{Attribute}:
  \item \br{BayesException}:
  \item \br{ClassSummary}:
  \item \br{ContinuousAttribute}:
  \item \br{DiscreteAttribute}:
  \item \br{NaiveBayes}:
  \item \br{NaiveBayesModel}:
\end{enumerate}

@@

\begin{enumerate}
  \item \br{KNN}:
  \item \br{KNNModel}:
  \item \br{KNNException}:
\end{enumerate}

\section{Results}
\begin{tabular}{ |c|c|c|c|c|c| }
  ID3 & Adaboost on ID3 & Random Forest & Naive Bayes & Adaboost on Naive Bayes & K-Nearest Neighbor
\end{tabular}

>>>>

\newcommand{\bb}{\textbf}
\newcommand{\ii}{\textit}

\usepackage{natbib}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{algorithm2e}
\usepackage{parskip}
\usepackage{geometry}
\usepackage{enumitem}

@@

\section{Introduction}
This report details the experimental study conducted for the CS6735 programming project. Six machine learning algorithms were implemented, including both regular and ensemble learning algorithms. Each was evaluated on five datasets from the UCI Machine Learning data repository using 10 times 5-fold cross validation. The technical details of the implementation will be described in this report and the results will be presented and analyzed.

@@

\subsection{Naïve Bayes}
The Naïve Bayes algorithm is implemented as described in \cite{Mitchell:1997:ML:541177}. This algorithm is named due its assumption of conditional independence amongst each attribute:

@@

and its application of Bayes thereon:

@@

Naïve Bayes is a practical learning algorithm, receives relatively good results given its preference bias and is easy to implement. This algorithm naturally handles both categorical and continuous data (given a prior is assumed). For each continuous attribute, a Gaussian distribution was assumed. The final algorithm implemented was:

$$\hat{y}= \mathrm{argmax}_{k\in\{1,..K\}} P(v_k)\prod_{i=1}^mp\left(a_i|v_k\right)\prod_{j=m}^nP\left(a_j|v_k\right)$$

where $P$ is the probability, $p$ is the gaussian probability density function and $K$ is the number of distinct targets. In this equation, the first m attributes are continuous whereas the later are catigorical. During training, the data $S$ is split by lables into subsets ${S_1,...,S_n}$ where $n$ is the number of different classes. For each subset, we estimate the class probability $P(v_k)$. Subsequently, for each attribute value $a_i$ of each attribute $a$, we estimate $P(a_i|v_k)$ or $p$. We are not able to immediately calculate $p(a_i|v_k)$ as attribute $a$ is a continous attribute.

@@

The primary part of the algorithm is to maintain a weight value $w$ for every sample within the data $S$. This value increases when the sample is misclassified and decreases when the sample is correctly classified. The target values are assumed be to in the set ${+1, -1}$. The Adaboost algorithm is easily implemented on weak learners which are parameterized by sample weights. Neither Naïve Bayes or ID3 natively implement weighted training. Therefore, an alternative implementation was used where a subset of the training data is selected with replacement based on the weights. For example, if the weight vector for two samples is ${1, 2}$, the second sample is twice as likely to be picked each time.

@@

To implement multiclass adaboost, $K$ adaboost models are trained where $K$ is the total number of distant classes. For each adaboost model, one target is selected as the $+1$ adaboost target and the other become the $-1$ target. The target value associated with the most positive prediction becomes the predicted class.

\subsubsection{Adaboost on Naïve Bayes}
Naïve Bayes is an inherently weak learner due to its assumption of conditional independence amongst attributes. This fact introduces a large amount of preference bias which makes a Naïve Bayes and ideal candidate for the Adaboost algorithm.

\subsubsection{Adaboost on ID3}
The ID3 algorithm does not introduce a large amount of preference bias and often overfitting if allowed to train to completion. Therefore, to implement Adaboost on ID3, the depth of the trees were limited to one level. This type of tree is known as a \ii{decision stump}.

\subsection{Random Forest}
Random forest algorithm is a bagging algorithm which uses an ensemble of strong learners to reduce overfitting to the training set. This method contains many similarities to the adaboost algorithm as described in section \ref{adaboost}; however, no weights are used for random forests. For a predefined number of iterations, a subset of the of the training data is selected with replacement. The new training set is then used to train a decision tree to completion and added to tree is added to a list. To make a classification, each tree in the forest votes and the most common target value becomes the predicted class. As an extension of the base random forest algorithm, weights may be given to each decision tree based on their classification error during training; however, this extension was not added for this implementation.

\subsection{K-Nearest Neighbors}
The K-Nearest Neighbor algorithm is an instance based learning algorithm which makes predictions by finding the $k$ nearest neighbors of a sample $x$ and using the most common class as the predicted class for that sample. This algorithm can be used with both categorical and continuous data. For this implementation, Euclidian distance was used for continuous variables and Hamming distance was used for categorical data.

@@

\subsection{Breast Cancer Data}
\begin{itemize}[leftmargin=*]
  \item[] \bb{Title}: Wisconsin Diagnostic Breast Cancer
  \item[] \bb{Date}: November 1995
  \item[] \bb{Number of Samples}: 569
  \item[] \bb{Number of Attributes}: 10
  \item[] \bb{Attribute Information}:
  \item[]
  \begin{tabular}{l c c c }
    \bb{Description}             & \bb{Values} & \bb{Type} \\
    Sample Code Number           & id number   & Discrete  \\
    Clump Thickness              & 1 - 10      & Discrete  \\
    Uniformity of Cell Size      & 1 - 10      & Discrete  \\
    Uniformity of Cell Shape     & 1 - 10      & Discrete  \\
    Marginal Adhesion            & 1 - 10      & Discrete  \\
    Single Epithelial Cell Size  & 1 - 10      & Discrete  \\
    Bare Nuclei                  & 1 - 10      & Discrete  \\
    Bland Chromatin              & 1 - 10      & Discrete  \\
    Normal Nucleoli              & 1 - 10      & Discrete  \\
    Mitoses                      & 1 - 10      & Discrete
  \end{tabular}
  \item[] \bb{Class Target}: Neoplasm
  \item[] \bb{Class Information}:
  \item[]
  \begin{tabular}{l c c c c }
    \bb{Description} & \bb{Value} & \bb{Count} & \bb{Percentage} \\
    Benign           & 2          & 357        & 65.5\%          \\
    Malignant        & 4          & 212        & 34.5\%
  \end{tabular}
  \item[] \bb{Missing Attributes}: 16
\end{itemize}

\subsection{Car Data}
\begin{itemize}[leftmargin=*]
  \item[] \bb{Title}: Car Evaluation Database
  \item[] \bb{Date}: June 1997
  \item[] \bb{Number of Samples}: 1728
  \item[] \bb{Number of Attributes}: 6
  \item[] \bb{Attribute Information}:
  \item[]
  \begin{tabular}{l c c c }
    \bb{Description} & \bb{Values}            & \bb{Type} \\
    buying           & v-high, high, med, low & Discrete  \\
    maint            & v-high, high, med, low & Discrete  \\
    doors            & 2, 3, 4, 5-more        & Discrete  \\
    persons          & 2, 4, more             & Discrete  \\
    lug\_boot        & small, med, big        & Discrete  \\
    safety           & low, med, high         & Discrete
  \end{tabular}
  \item[] \bb{Class Target}: Car Quality
  \item[] \bb{Class Information}:
  \item[]
  \begin{tabular}{l c c c c }
    \bb{Description} & \bb{Value} & \bb{Count} & \bb{Percentage} \\
    Unacceptable     & unacc      & 1210       & 70.023\%        \\
    Acceptable       & acc        & 384        & 22.222\%        \\
    Good             & good       & 69         & 3.993\%         \\
    Very Good        & v-good     & 65         & 3.762\%
  \end{tabular}
  \item[] \bb{Missing Attributes}: none
\end{itemize}

\subsection{E. Coli Data}
\begin{itemize}[leftmargin=*]
  \item[] \bb{Title}: Protein Localization Sites
  \item[] \bb{Date}: September 1997
  \item[] \bb{Number of Samples}: 336
  \item[] \bb{Number of Attributes}: 8
  \item[] \bb{Attribute Information}:
  \item[]
  \begin{tabular}{l c c c }
    \bb{Description} & \bb{Values}       & \bb{Type}  \\
    Sequence Name    &  Accession Number & Discrete   \\
    mcg              & 0.00 - 0.89       & Continuous \\
    gvh              & 0.16 - 1.00       & Continuous \\
    lip              & 0.48 - 1.00       & Discrete   \\
    chg              & 0.50 - 1.00       & Discrete   \\
    aac              & 0.00 - 0.88       & Continuous \\
    alm1             & 0.03 - 1.00       & Continuous \\
    alm2             & 0.00 - 0.99       & Continuous
  \end{tabular}
  \item[] \bb{Class Target}:  Localization Site
  \item[] \bb{Class Information}:
  \item[]
  \begin{tabular}{l c c c c }
    \bb{Description}           & \bb{Value} & \bb{Count} & \bb{Percentage} \\
    Cytoplasm                  & cp         & 143        & 42.56\%         \\
    Inner Membrane             & im         & 77         & 22.92\%         \\
    Perisplasm                 & pp         & 52         & 15.48\%         \\
    Inner Membrane Uncleavable & imU        & 35         & 10.42\%         \\
    Outer Membrane             & om         & 20         & 5.95\%          \\
    Outer Membrane             & omL        & 5          & 1.49\%          \\
    Inner Membrane Lipoprotein & imL        & 2          & 0.59\%          \\
    Inner Membrane Cleavable   & imS        & 2          & 0.59\%
  \end{tabular}
  \item[] \bb{Missing Attributes}: none
\end{itemize}

\subsection{Letter Recognition Data}
\begin{itemize}[leftmargin=*]
  \item[] \bb{Title}: Letter Image Recognition Data
  \item[] \bb{Date}: January 1991
  \item[] \bb{Number of Samples}: 20000
  \item[] \bb{Number of Attributes}: 16
  \item[] \bb{Attribute Information}:
  \item[]
  \begin{tabular}{l c c c }
    \bb{Description} & \bb{Values}            & \bb{Type}  \\
    x-box	           & 0 - 9                  & Continuous \\
    y-box	           & 0 - 9                  & Continuous \\
    width	           & 0 - 9                  & Continuous \\
    high 	           & 0 - 9                  & Continuous \\
    onpix	           & 0 - 9                  & Continuous \\
    x-bar	           & 0 - 9                  & Continuous \\
    y-bar	           & 0 - 9                  & Continuous \\
    x2bar	           & 0 - 9                  & Continuous \\
    y2bar	           & 0 - 9                  & Continuous \\
    xybar	           & 0 - 9                  & Continuous \\
    x2ybr	           & 0 - 9                  & Continuous \\
    xy2br	           & 0 - 9                  & Continuous \\
    x-ege	           & 0 - 9                  & Continuous \\
    xegvy	           & 0 - 9                  & Continuous \\
    y-ege	           & 0 - 9                  & Continuous \\
    yegvx	           & 0 - 9                  & Continuous
  \end{tabular}
  \item[] \bb{Class Target}: Letter
  \item[] \bb{Class Information}:
  \item[]
  \begin{tabular}{l c c c c }
    \bb{Description} & \bb{Value} & \bb{Count} & \bb{Percentage} \\
    Letter A                & A          & 789        & 0.04\% \\
    Letter B                & B          & 766        & 0.04\% \\
    Letter C                & C          & 736        & 0.04\% \\
    Letter D                & D          & 805        & 0.04\% \\
    Letter E                & E          & 768        & 0.04\% \\
    Letter F                & F          & 775        & 0.04\% \\
    Letter G                & G          & 773        & 0.04\% \\
    Letter H                & H          & 734        & 0.04\% \\
    Letter I                & I          & 755        & 0.04\% \\
    Letter J                & J          & 747        & 0.04\% \\
    Letter K                & K          & 739        & 0.04\% \\
    Letter L                & L          & 761        & 0.04\% \\
    Letter M                & M          & 792        & 0.04\% \\
    Letter N                & N          & 783        & 0.04\% \\
    Letter O                & O          & 753        & 0.04\% \\
    Letter P                & P          & 803        & 0.04\% \\
    Letter Q                & Q          & 783        & 0.04\% \\
    Letter R                & R          & 758        & 0.04\% \\
    Letter S                & S          & 748        & 0.04\% \\
    Letter T                & T          & 796        & 0.04\% \\
    Letter U                & U          & 813        & 0.04\% \\
    Letter V                & V          & 764        & 0.04\% \\
    Letter W                & W          & 752        & 0.04\% \\
    Letter X                & X          & 787        & 0.04\% \\
    Letter Y                & Y          & 786        & 0.04\% \\
    Letter Z                & Z          & 734        & 0.04\%
  \end{tabular}
  \item[] \bb{Missing Attributes}: none
\end{itemize}

\subsection{Mushroom Data}
\begin{itemize}[leftmargin=*]
  \item[] \bb{Title}: Mushroom Database
  \item[] \bb{Date}: 27 April 1987
  \item[] \bb{Number of Samples}: 8124
  \item[] \bb{Number of Attributes}: 22
  \item[] \bb{Attribute Information}:
  \item[]
  \begin{tabular}{l c c c }
    \bb{Description}         & \bb{Values}             & \bb{Type} \\
    cap-shape                & b,c,x,f,k,s             & Discrete  \\
    cap-surface              & f,g,y,s                 & Discrete  \\
    cap-color                & n,b,c,g,r,p,u,e,w,y     & Discrete  \\
    bruises?                 & t,f                     & Discrete  \\
    odor                     & a,l,c,y,f,m,n,p,s       & Discrete  \\
    gill-attachment          & a,d,f,n                 & Discrete  \\
    gill-spacing             & c,w,d                   & Discrete  \\
    gill-size                & b,n                     & Discrete  \\
    gill-color               & k,n,b,h,g,r,o,p,u,e,w,y & Discrete  \\
    stalk-shape              & e,t                     & Discrete  \\
    stalk-root               & b,c,u,e,z,r,?           & Discrete  \\
    stalk-surface-above-ring & f,y,k,s                 & Discrete  \\
    stalk-surface-below-ring & f,y,k,s                 & Discrete  \\
    stalk-color-above-ring   & n,b,c,g,o,p,e,w,y       & Discrete  \\
    stalk-color-below-ring   & n,b,c,g,o,p,e,w,y       & Discrete  \\
    veil-type                & p,u                     & Discrete  \\
    veil-color               & n,o,w,y                 & Discrete  \\
    ring-number              & n,o,t                   & Discrete  \\
    ring-type                & c,e,f,l,n,p,s,z         & Discrete  \\
    spore-print-color        & k,n,b,h,r,o,u,w,y       & Discrete  \\
    population               & a,c,n,s,v,y             & Discrete  \\
    habitat                  & g,l,m,p,u,w,d           & Discrete
  \end{tabular}
  \item[] \bb{Class Target}: Edibility
  \item[] \bb{Class Information}:
  \item[]
  \begin{tabular}{l c c c c }
    \bb{Description} & \bb{Value} & \bb{Count} & \bb{Percentage} \\
    Edible           & e          & 4208       & 51.80\%        \\
    Poisonous        & p          & 3916       & 48.20\%
  \end{tabular}
  \item[] \bb{Missing Attributes}: 2480 (all for attribute \#11)
\end{itemize}

\section{Technical Details}
Missing attribute values within the breast cancer dataset were replaced with the mode of the samples of the same class. For the mushroom dataset, as the amount of missing values for attribute 11 was very large, the missing values themselves were simply treated as another category. No discretization occurred as all base algorithms are able to handle continuous data. For all datasets, any sort of identification number or code attributes were removed. Within the E. Coli dataset, the lip and chg categorical attributes were also removed as they provided minimal information. Furthermore, any string values were converted to integers. For example, the ``v-high'', ``high'', ``med'' and ``low'' attribute values would have been converted to 0, 1, 2, 3 respectively.

\subsection{ID3}
\begin{tabular}{ |c|c|c| }
  Dataset            & Max Level & Minimum \# of Samples \\
  Breast Cancer      & None      & SOMETHING            \\
  Car Cancer         & None      & SOMETHING            \\
  Letter Recognition & None      & SOMETHING            \\
  E. Coli            & None      & SOMETHING            \\
  Mushroom           & None      & SOMETHING
\end{tabular}

\subsection{Naïve Bayes}
gaussian

\subsection{Adaboost on Naïve Bayes}
number of learners

@@

\begin{enumerate}[leftmargin=*]
  \item[] \bb{Algorithm}:
  \item[] \bb{Dataset}:
  \item[] \bb{Model}:
  \item[] \bb{KFold}: Implements the KFold cross validation algorithm.
  \item[] \bb{Report}: The object returned from a k-fold cross validation test....
  \item[] \bb{Util}: Utility functions used through the machine learning project.
\end{enumerate}

@@

\begin{enumerate}[leftmargin=*]
  \item[] \bb{Children}:
  \item[] \bb{ID3}:
  \item[] \bb{ID3Model}:
  \item[] \bb{Node}:
\end{enumerate}

@@

\begin{enumerate}[leftmargin=*]
  \item[] \bb{Adaboost}:
  \item[] \bb{AdaboostModel}:
  \item[] \bb{Multi-Adaboost}:
  \item[] \bb{Multi-AdaboostModel}:
  \item[] \bb{RandomForest}:
  \item[] \bb{RandomForstModel}:
\end{enumerate}

@@

\begin{enumerate}[leftmargin=*]
  \item[] \bb{AttributeException}:
  \item[] \bb{DataException}:
  \item[] \bb{FileException}:
  \item[] \bb{PredictionException}:
\end{enumerate}

@@

\begin{enumerate}[leftmargin=*]
  \item[] \bb{MathException}:
  \item[] \bb{Matrix}:
  \item[] \bb{Tuple}:
  \item[] \bb{Util}:
  \item[] \bb{Vector}:
\end{enumerate}

@@

\begin{enumerate}[leftmargin=*]
  \item[] \bb{DistanceFunction}:
  \item[] \bb{Euclidian}:
  \item[] \bb{Hamming}:
\end{enumerate}

\subsubsection{distribution}
This package contains distribution implementations for the Naïve Bayes classifier.

\begin{enumerate}[leftmargin=*]
  \item[] \bb{Distribution}:
  \item[] \bb{GaussianDistribution}:
\end{enumerate}

\subsection{nb}
This package contains all of the objects associated with Naïve Bayes.

\begin{enumerate}[leftmargin=*]
  \item[] \bb{Attribute}:
  \item[] \bb{BayesException}:
  \item[] \bb{ClassSummary}:
  \item[] \bb{ContinuousAttribute}:
  \item[] \bb{DiscreteAttribute}:
  \item[] \bb{NaïveBayes}:
  \item[] \bb{NaïveBayesModel}:
\end{enumerate}

@@

\begin{enumerate}[leftmargin=*]
  \item[] \bb{KNN}:
  \item[] \bb{KNNModel}:
  \item[] \bb{KNNException}:
\end{enumerate}

\section{Results}
\begin{table}
  \begin{tabular}{ |c|c|c|c|c|c| }
    \hline
    Breast Cancer           & Car      & Letter   & E. Coli  & Mushroom \\ \hline
    Adaboost on ID3         & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
    ID3                     & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
    Random Forest           & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
    Naïve Bayes             & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
    Adaboost on Naïve Bayes & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
    K-Nearest Neighbor      & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
  \end{tabular}
  \caption{Results of the six implemented algorithms on five UCI Machine Learning repositories. Accuracy calculated using 10 times 5-fold cross validation.}
\end{table}
